\textit{Supplementary materials for: } High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2020-06-02 paper/main.tex
WIP nat comm revision

@@

An open question not addressed by our study pertains to how different
structures integrate incoming information with different time
constants.  For example, one line of work suggests that the cortical
surface comprises a structured map such that nearby brain structures
process incoming information at similar timescales.  Low-level sensory
areas integrate information relatively quickly, whereas higher-level
regions integrate information relatively slowly~\citep{BaldEtal17,
  HassEtal08, HassEtal15, HoneEtal12a, LernEtal11, LernEtal14}.  Other
related work in human and mouse brains indicates that the temporal
response profile of a given brain structure may relate to how strongly
connected that structure is with other brain
areas~\citep{FallEtal19}.  Further study is needed to understand the
role of temporal integration at different scales of network
interaction, and across different anatomical structures.

>>>>

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/higher_order_sims}
  \caption{\textbf{Recovery of simulated first and second order dynamic correlations.}  Each panel displays the average correlations
    between the vectorized upper triangles of the recovered
    correlation matrix and the simulated correlation matrix at each
    timepoint and for each synthetic dataset.  (The averages are taken across 10 different
    randomly generated synthetic datasets of the given category.)
    Error ribbons denote 95\% confidence intervals (taken across
    datasets).  For a complete description of each synthetic dataset,
    see \textit{Synthetic data}.  \textbf{a. Constant correlations.}
    These first and second order dynamic correlation were
    simulated from datasets have a stable (unchanging) underlying correlation
    matrix.  \textbf{b. Random correlations.}  These first and second order dynamic correlation were
    simulated from datasets are
    generated using a new independently drawn correlation matrix at
    each new timepoint.  \textbf{c. Ramping correlations.}  These first and second order dynamic correlation were
    simulated from
    datasets are generated by smoothly varying the underlying
    correlations between the randomly drawn correlation matrices at
    the first and last timepoints and displays the
    correlations between the recovered dynamic correlations and the
  simualted correlation first and second order correlation matrices.   \textbf{d. Event-based correlations.}  These first and second order dynamic correlation were
    simulated from datasets are
    each generated using five randomly drawn correlation matrices that
    each remain stable for a fifth of the total timecourse.  }
  \label{fig:higherr_order_sims}
\end{figure}

@@

An open question not addressed by our study pertains to how different
structures integrate incoming information with different time
constants.  For example, one line of work suggests that the cortical
surface comprises a structured map such that nearby brain structures
process incoming information at similar timescales.  Low-level sensory
areas integrate information relatively quickly, whereas higher-level
regions integrate information relatively slowly~\citep{BaldEtal17,
  HassEtal08, HassEtal15, HoneEtal12a, LernEtal11, LernEtal14, ChieHone19}.  Other
related work in human and mouse brains indicates that the temporal
response profile of a given brain structure may relate to how strongly
connected that structure is with other brain
areas~\citep{FallEtal19}.  Further study is needed to understand the
role of temporal integration at different scales of network
interaction, and across different anatomical structures.

### 2020-06-02 paper/supporting_information.tex
WIP nat comm revision

>>>>

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/decode_levels_kernels}
\caption{\textbf{Across-participant decoding accuracy varies with
      correlation order and cognitive engagement across kernels}  \textbf{a-d..~Decoding accuracy as a function of order: PCA.}\textit{Order} ($x$-axis) refers to the maximum order of dynamic
    correlations that were available to the classifiers (see
    \textit{Feature weighting and testing}).  The reported
    across-participant decoding accuracies are averaged over all
    kernel shapes and widths (see \textit{Identifying robust decoding
      results}).  The $y$-values are displayed relative to chance
    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
    denote 95\% confidence intervals across cross-validation folds
    (i.e., random assignments of participants to the training and test
    sets).  The colors denote the experimental condition.  Arrows
    denote sets of features that yielded reliably higher (upwards
    facing) or lower (downward facing) decoding accuracy than the mean
    of all other features (via a two-tailed test, thresholded at
    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
    comparisons between the decoding accuracies achieved using
    different sets of neural features.  The circled values represent
    the maximum decoding accuracy within each experimental condition.)}
\label{fig:supp_kernels}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/decode_levels_widths}
\caption{\textbf{Top terms associated with the endpoints of the
    strongest correlations for the \textit{intact} experimental
    condition.}  Each color corresponds to one order of inter-subject
functional correlations. The inflated brain plots display the
locations of the endpoints of the 10 strongest (absolute value)
correlations at each order, projected onto the cortical
surface~\citep{CombEtal19}.  The lists of terms display
the top 10 Neurosynth terms~\citep{RubiEtal17} decoded from the
corresponding brain maps for each order.  (Also see Fig.~\neurosynth,
top row, in the main text.)}
\label{fig:supp_widths}
\end{figure}
